Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-01-03 survey/survey.tex
add a comment so that it doesn't get lost
add an abstract.

\begin{document}
\maketitle

@@

>>>>

\begin{document}
\begin{abstract}
  Our main models of computation (Turing Machines, RAM, but also
  modern computer architecture) make some fundamental assumptions about
  which operations are available: logical operations like conjunction,
  disjunction and negation, as well as reading and writing to a
  (large) collection to memory locations. While this conforms to
  a macro-level view of physics, it does not mesh as well with
  other views; in particular, both from a thermodynamic and a
  quantum view, these models are flawed. Both latter views of
  physics imply that information is a quantity that is conserved.

  We first define what information, and its conservation, means
  in a computational setting. This emphasizes the idea that
  computations, whatever they are, must be reversible. Thinking
  geometrically, we can think of programs as reversible deformations
  of data. From this fundamental idea, we rebuild notions of data
  and programs which, by construction, are reversible. After a
  brief overview of what this means for unstructured finite data,
  we dive into the main topic: a foundational reversible programming
  language. We re-examine the Curry-Howard correspondence, as the
  classical correspondence is not reversible. This allows us to
  establish a new correspondence, this time between a reversible
  programming language for witnessing type isomorphisms and
  proof terms for commutative semirings, which is sound and
  complete for finite types.

  We then ``move up a level'' to examine what it means for a
  program to be reversible when its data is a program. This
  gives a notion of reversible program equivalence. To get
  something sound and complete, we must look at a ``higher 
  dimensional'' analog to commutative semirings: symmetric
  Rig Groupoids. The coherence laws for these are exactly the
  reversible program equivalences we sought.

  Something about Theseus?

\end{abstract}

\maketitle

@@

\jc{We should decide what you level convention is. Do we say
that $\iso$ is level 0, so that $\Leftrightarrow$ is level 1?
We need to be consistent about it.}
